---
title: "HDDM PLOTS"
output: rmarkdown::github_document
---
test
This notebook was created to plot the hddm parameter outputs for Experiment 1 and Experiment 2 of the Dot Motion task switching paper, with the two interactions Asymmetric switch costs and Switch Costs : Response Congruency.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(data.table)
library(ggplot2)
library(gridExtra)
```
First we will create data tables with all the effects from the model fits. 

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Parameters: 
plot_size = 24

# Main Effects:
# 1. Switch Costs
DT_Switch_Cost = data.table(SC = c("Switch Cost","Switch Cost"), Experiment = c("Exp1", "Exp2"), fit = c(-0.414, -0.316), lower = c(-0.487, -0.387), upper = c(-0.340, -0.245)) 
DT_Switch_Cost_Threshold = data.table(SC = c("Switch Cost","Switch Cost"), Experiment = c("Exp1", "Exp2"), fit = c(0.063, 0.1168), lower = c(0.029, 0.083), upper = c(0.096, 0.150)) 

# 2. Task
DT_Task_drift = data.table(SC = c("task","task"), Experiment = c("Exp1", "Exp2"), fit = c(0.342, 0.0037), lower = c(0.22386096, -0.11592849), upper = c(0.46148086, 0.1180223)) # p value < 0.001 Exp2 p = 0.4734
DT_Task_threshold = data.table(SC = c("task","task"), Experiment = c("Exp1", "Exp2"), fit = c(-0.026711213372, 0.138670287342), lower = c(-0.07894858, 0.08645048), upper = c(0.02462728, 0.19032629)) # 

# 3.Congruency
DT_congruency = data.table(SC = c("incongruency","incongruency"), Experiment = c("Exp1", "Exp2"), fit = c(-0.480141688309, -0.374055233136), lower = c(-0.40468217, -0.3134809), upper = c(-0.55646391, -0.43782279)) # p value < 0.001 Exp2 p = 0.4734
DT_congruency_threshold = data.table(SC = c("incongruency","incongruency"), Experiment = c("Exp1", "Exp2"), fit = c(-0.101363625202, -0.0979685862689), lower = c(-0.0728155, -0.06767293), upper = c(-0.1318213,-0.13013283)) # p value < 0.001 & p value < 0.001

# Interactions:
# 1. Asymmetric Switch Costs
DT_SC_Task = data.table(SC = c("ASC","ASC"), Experiment = c("Exp1", "Exp2"), fit = c(-0.281, 0.02166), lower = c(-0.423, -0.12), upper = c(-0.132, 0.1538)) 
DT_SC_Task_Threshold = data.table(SC = c("ASC","ASC"), Experiment = c("Exp1", "Exp2"), fit = c(-0.0267, 0.138670287342), lower = c(-0.0789, 0.08645048), upper = c(0.0246, 0.19032629)) 

# 2. Switch Costs : Response Congruency
DT_Switch_Cost_Congruency = data.table(SC = c("SCRC","SCRC"), Experiment = c("Exp1", "Exp2"), fit = c(-0.272, -0.2023), lower = -c(0.154, 0.0939), upper = -c(0.390, 0.332))  
DT_Switch_Cost_Congruency_Threshold = data.table(SC = c("SCRC","SCRC"), Experiment = c("Exp1", "Exp2"), fit = c(-0.0668, -0.0526), lower = -c(0.014, -0.00306337), upper = -c(0.118, 0.11610236))  
```


Plot Switch Costs for Exp1 & Exp2

```{r}

my_hddm_plot = function(data_table, drift_or_threshold){#plot_size, dodge_width, errorbar_size)

P = ggplot(data_table) + aes(data_table =  SC, y = fit, fill=Experiment) + geom_col(aes(SC),color = "black", position=position_dodge(width = 0.5), width = 0.5) +
  scale_fill_manual(values=c('white','lightgray')) + 
  geom_errorbar(data = data_table, aes(SC, ymin = lower, ymax = upper) , width=.2, size = 0.9, position=position_dodge(width = 0.5))+
  xlab("Switch Cost") + 
   ylab(drift_or_threshold) +
   ggtitle("") + 
   theme(plot.title = element_text(lineheight=3, face="bold", color="black", size=plot_size))+
   theme(axis.ticks=element_blank(),axis.title.x=element_blank(), axis.text.y = element_text(size=plot_size,color="black"), text = element_text(size = plot_size), axis.text.x =  element_text(color = "black", size = plot_size), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank()) + theme(legend.title = element_blank())  +  theme(legend.position="none")+
   theme(axis.line.x = element_line(color="black", size = 0.5),
         axis.line.y = element_line(color="black", size = 0.5)) +geom_hline(yintercept = 0)

return(P)
}
```

```{r}

my_hddm_plot_legend = function(data_table, drift_or_threshold){#plot_size, dodge_width, errorbar_size)

P = ggplot(data_table) + aes(data_table =  SC, y = fit, fill=Experiment) + geom_col(aes(SC),color = "black", position=position_dodge(width = 0.5), width = 0.5) +
  scale_fill_manual(values=c('white','lightgray')) + 
  geom_errorbar(data = data_table, aes(SC, ymin = lower, ymax = upper) , width=.2, size = 0.9, position=position_dodge(width = 0.5))+
  xlab("Switch Cost") + 
   ylab(drift_or_threshold) +
   ggtitle("") + 
   theme(plot.title = element_text(lineheight=3, face="bold", color="black", size=plot_size))+
   theme(axis.ticks=element_blank(),axis.title.x=element_blank(), axis.text.y = element_text(size=plot_size,color="black"), text = element_text(size = plot_size), axis.text.x =  element_text(color = "black", size = plot_size), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank()) + theme(legend.title = element_blank())  +  theme(legend.position="none")+
   theme(axis.line.x = element_line(color="black", size = 0.5),
         axis.line.y = element_line(color="black", size = 0.5)) +geom_hline(yintercept = 0)+
   theme(legend.position = c(0.8, 0.08), legend.title = element_blank())

return(P)
}
```

```{r}

my_hddm_plot_task_legend = function(data_table, drift_or_threshold, XLAB){#plot_size, dodge_width, errorbar_size)

P = ggplot(data_table) + aes(data_table =  SC, y = fit, fill=Experiment) + geom_col(aes(SC),color = "black", position=position_dodge(width = 0.5), width = 0.5) +
  scale_fill_manual(values=c('red','lightblue')) + 
  geom_errorbar(data = data_table, aes(SC, ymin = lower, ymax = upper) , width=.2, size = 0.9, position=position_dodge(width = 0.5))+
  xlab("Switch Cost") + 
   ylab(drift_or_threshold) +
   ggtitle("") + 
   theme(plot.title = element_text(lineheight=3, face="bold", color="black", size=plot_size))+
   theme(axis.ticks=element_blank(),axis.title.x=element_blank(), axis.text.y = element_text(size=plot_size,color="black"), text = element_text(size = plot_size), axis.text.x =  element_text(color = "black", size = plot_size), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank()) + theme(legend.title = element_blank())  +  theme(legend.position="none")+
   theme(axis.line.x = element_line(color="black", size = 0.5),
         axis.line.y = element_line(color="black", size = 0.5)) +geom_hline(yintercept = 0)+
   theme(legend.position = c(0.8, 0.8), legend.title = element_blank())

return(P)
}
```

```{r}

my_hddm_plot_task_legend2 = function(data_table, drift_or_threshold, XLAB){#plot_size, dodge_width, errorbar_size)

P = ggplot(data_table) + aes(data_table =  SC, y = fit, fill=Experiment) + geom_col(aes(SC),color = "black", position=position_dodge(width = 0.5), width = 0.5) +
  scale_fill_manual(values=c('red','lightblue')) + 
  geom_errorbar(data = data_table, aes(SC, ymin = lower, ymax = upper) , width=.2, size = 0.9, position=position_dodge(width = 0.5))+
  xlab("Switch Cost") + 
   ylab(drift_or_threshold) +
   ggtitle("") + 
   theme(plot.title = element_text(lineheight=3, face="bold", color="black", size=plot_size))+
   theme(axis.ticks=element_blank(),axis.title.x=element_blank(), axis.text.y = element_text(size=plot_size,color="black"), text = element_text(size = plot_size), axis.text.x =  element_text(color = "black", size = plot_size), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank()) + theme(legend.title = element_blank())  +  theme(legend.position="none")+
   theme(axis.line.x = element_line(color="black", size = 0.5),
         axis.line.y = element_line(color="black", size = 0.5)) +geom_hline(yintercept = 0)+
   theme(legend.position = c(0.8, 0.08), legend.title = element_blank())

return(P)
}
```

```{r}

my_hddm_plot_task = function(data_table, drift_or_threshold){#plot_size, dodge_width, errorbar_size)

P = ggplot(data_table) + aes(data_table =  SC, y = fit, fill=Experiment) + geom_col(aes(SC),color = "black", position=position_dodge(width = 0.5), width = 0.5) +
  scale_fill_manual(values=c('red','lightblue')) + 
  geom_errorbar(data = data_table, aes(SC, ymin = lower, ymax = upper) , width=.2, size = 0.9, position=position_dodge(width = 0.5))+
  xlab("Switch Cost") + 
   ylab(drift_or_threshold) +
   ggtitle("") + 
   theme(plot.title = element_text(lineheight=3, face="bold", color="black", size=plot_size))+
   theme(axis.ticks=element_blank(),axis.title.x=element_blank(), axis.text.y = element_text(size=plot_size,color="black"), text = element_text(size = plot_size), axis.text.x =  element_text(color = "black", size = plot_size), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank()) + theme(legend.title = element_blank())  +  theme(legend.position="none")+
   theme(axis.line.x = element_line(color="black", size = 0.5),
         axis.line.y = element_line(color="black", size = 0.5)) +geom_hline(yintercept = 0)

return(P)
}
```

Now we create the plots we want.
First, main Effect for Switch Costs for (1) drift rate and (2) threshold
```{r}
SC_drift = my_hddm_plot_legend(DT_Switch_Cost, "drift rate")
SC_threshold = my_hddm_plot(DT_Switch_Cost_Threshold, "threshold")
# put both plots on the same grid
grid.arrange(SC_drift, SC_threshold, nrow = 1, ncol = 2)
```

Second, main Effect for Task for (1) drift rate and (2) threshold

```{r}
Task_drift = my_hddm_plot_task_legend(DT_Task_drift, "drift rate")
Task_threshold = my_hddm_plot_task(DT_Task_threshold, "threshold")
# put both plots on the same grid
grid.arrange(Task_drift, Task_threshold, nrow = 1, ncol = 2)
```

```{r}
grid.arrange(SC_drift, SC_threshold,Task_drift, Task_threshold, nrow = 2, ncol = 2)
```

Third, main Effect for Congruency for (1) drift rate and (2) threshold

```{r}
#Congruency_drift = my_hddm_plot(DT_congruency, "drift rate")
#Congruency_threshold = my_hddm_plot(DT_congruency_threshold, "threshold")
# put both plots on the same grid
#grid.arrange(Congruency_drift, Congruency_threshold, nrow = 1, ncol = 2)
```

Now the 2 interactions:
First, asymmetric switch costs for (1) drift rate and (2) threshold

```{r}
SC_Task = my_hddm_plot_task_legend2(DT_SC_Task, "drift rate")
SC_Task_Threshold = my_hddm_plot_task(DT_SC_Task_Threshold, "threshold")
# put both plots on the same grid
grid.arrange(SC_Task, SC_Task_Threshold, nrow = 1, ncol = 2)
```

Second, switch costs & response congruence for (1) drift rate and (2) threshold

```{r}
Switch_Cost_Congruency = my_hddm_plot_legend(DT_Switch_Cost_Congruency, "drift rate")
Switch_Cost_Congruency_Threshold = my_hddm_plot(DT_Switch_Cost_Congruency_Threshold, "threshold")
# put both plots on the same grid
grid.arrange(Switch_Cost_Congruency, Switch_Cost_Congruency_Threshold, nrow = 1, ncol = 2)
```


```{r}

grid.arrange(SC_Task, SC_Task_Threshold,Switch_Cost_Congruency, Switch_Cost_Congruency_Threshold, nrow = 2, ncol = 2)

```