
---
title: "R Tutorial Freiburg "
output:
  pdf_document: default
  html_notebook: default
  word_document: default
---
R notebook to analyse Voluntary Task Switching Data.

First, load libraries (if not loaded before do install.packages("") e.g. install.packages("data.table"))
```{r}
library(data.table)
library(lme4)
library(effects)
library(ggplot2)

```

Now, we lead the csv file from the path where it is (you have to change the path to your path).
Each row is one trial.
subject_id discribes the id of teh subject.
rt is reachtion time of the trial
correct: 1 is correct 0 is innncorrect
taskTransition: 1 is switch trials 0 is repeat trials
last_trial_correct: 0 is incorrect 1 is correct
yoked_error: 1 ERROR AFTER CORRECT TRIAL
pre_yoked_error: 1 one trial before yoked_error
pre_pre_yoked_error: 2 trials before yoked_error
post_yoked_error: trial after yoked_error

difficulty_increase: TRUE means that the task ws getting harder on this trial

```{r}
d <- fread('~/Desktop/Freiburg/jupyter/VTS_4.csv', na.strings="NaN")
d

```

now let's only include rt's longer than 200ms
```{r}
d1 = subset(d,  rt > 200)
hist(d1$rt, breaks = 50)
```
now we make things into factors

```{r}
d1[,taskTransition:=as.factor(taskTransition)]
levels(d1$taskTransition) <- c( "repeat","switch")
contrasts(d1$taskTransition) <- c(-0.5, 0.5)

d1
```

We want to find out if subjects have longer RTs when they switch between tasks, compared to when they repeat the tasks.

```{r}
model = lmer(rt ~ taskTransition + (1|subject_id), d1)
summary(model)
```

Extract the effect from the model.
```{r, echo=FALSE, warning=FALSE, message=FALSE}
e <- effect("taskTransition", model)
e2 <- as.data.frame(e) 
e2
```
Plot the effects.
```{r}
ggplot(e2, aes(x =  taskTransition, y = fit)) +
    geom_col(aes(taskTransition),color = "black") + 
    geom_errorbar(aes(taskTransition, ymin= c(e2[1,4], e2[2,4]), ymax=c(e2[1,5], e2[2,5])), width=.2, size = 0.9, position=position_dodge(width = 0.5))




```


